\documentclass[10pt,colorlinks,urlcolor=gray]{moderncv}

\moderncvtheme[blue, modroman]{classic}
\usepackage{resume_kleinschmidt}

\name{Dave F.}{Kleinschmidt}
\email{dave.f.kleinschmidt@gmail.com}
\homepage{www.davekleinschmidt.com}
\social[gh][github.com/kleinschmidt]{github.com/kleinschmidt}

\begin{document}

\makecvtitle

I'm a software engineer, data scientist, and cognitive scientist with more than
10 years of experience making complex ideas, data, and systems legible to
experts and beginners alike.  I have a track record of shipping software that
people actually use, a passion for making computational tools broadly useful for
humans through open source software, and a knack for straightforward and
intuitive presentation of difficult computational ideas in both software and
written/oral forms.

\section{Experience}

\cventry{2022--present}{Senior Algorithm/Research Software Engineer} {Beacon
  Biosignals}{Remote}{}{As IC and tech lead of Quantitative Tools Team, built
  out Beacon's \textbf{platform for algorithm development and quantitative
    work}: data provenance/versioning system used by all algorithm and life
  science teams, distributed ML training/evaluation capability, distributed
  batch building for large time-series biosignal datasets
  (\href{https://github.com/beacon-biosignals/OndaBatches.jl}{OndaBatches.jl}).
  Tech lead for
  \href{https://github.com/beacon-biosignals/ray_core_worker_julia_jll.jl}{Julia-language
    runtime} for \href{https://Ray.io}{Ray.io}.}

\cventry{2021--2022}{Research Scientist}{Beacon Biosignals}{Remote}{}{Developed,
  applied, and interpreted novel statistical and machine learning models to
  provide insight into human EEG data for clinical and industry partners.  Tech
  lead and project manager for quantitative science team handling Beacon's first
  large contract: cleaned, featurized, and analyzed 10,000s of overnight EEG
  recordings from a Phase 3 clinical trial.}

\cventry{2013--present}{Open source maintainer}{JuliaStats
  organization}{Distributed/remote}{}{Maintain and develop open source software
  for statistical modeling in the Julia language.  Write code and documentation,
  review contributions, manage releases and automated testing/CI.  Primary
  developer of \textbf{StatsModels.jl},
  \href{https://juliahub.com/ui/Packages/StatsModels/4MFnV/0.6.13?t=2}{used in
    100+ packages} to transform tabular data to numerical arrays.}

\cventry{2018--2021}{Assistant Professor of Psychology}{Rutgers
  University}{New Brunswick, NJ}{}{Directed computational cognitive science lab;
  Supervised graduate research assistants and staff.  Designed, implemented (custom
  node.js+MongoDB backend), and analyzed data (using R and Julia) from \textbf{online
    behavioral experiments}.  Designed and implement machine learning models of
  cognition.}

\cventry{2016--2018}{CV Starr Postdoctoral Fellow}{Princeton Neuroscience
  Institute}{Princeton, NJ}{}{Implemented \textbf{custom Bayesian nonparametric
    models} of human perception and categorization.  Co-designed and ran \textbf{weekly
  open workshop on statistical philosophy and methods} for PhD students and other
  post-docs (regression, hierarchical models, Bayesian methods)}

\cventry{2010--2016}{PhD research}{Brain and Cognitive Sciences, University of
  Rochester}{Rochester, NY}{}{Created \textbf{novel Bayesian theory of
    perceptual learning for speech}, implemented with MCMC sampler in custom R
  code and Stan.  Developed and deployed custom web-based auditory psychophysics
  experiments in javascript.  Lead machine learning analysis of multimodal data
  from brain imaging (fMRI) experiments of human perceptual learning.}

\cventry{2009--2010}{Baggett Fellow}{Linguistics, University of
  Maryland}{College Park, MD}{}{Designed and taught one-day \textbf{workshop on
    mixed-effects models and ANOVA}.  Research on penalized matrix factorization
  (sparse coding) models of statistical learning}

\section{Education}
\label{sec:education}

\cventry{2010--2016}{Ph.D. Brain and Cognitive Sciences}{University of
  Rochester}{Rochester, NY}{}{}
\cventry{2005--2009}{B.A. Mathematics, concentration Cognitive Science}{Williams
  College}{Williamstown, MA}{\emph{Summa cum laude}, highest honors in Cognitive
  Science}{}

\section{Skills}

\cvcomputer{Statistics}{Linear/logistic regression, mixed-effects models,
  nonparametrics, Bayesian methods}{Distributed systems}{Kubernetes,
  stream/batch processing, Julia multiprocessing, Ray.io}

\cvcomputer{Software Engineering}{Git, Github (Actions), Docker, AWS (EC2, ECR, EKS, SQS),
  Arrow}{Machine Learning}{Predictive models, classification, clustering, NLP,
  deep learning}

\section{Programming Languages}

\cvcomputer{Julia}{DataFrames.jl, GLM.jl, MixedModels.jl,
  Makie.jl, Flux.jl}{R}{tidyverse (dplyr/purrr/tidyr),
  ggplot2, lme4/brms, rstan}

\cvcomputer{Python}{numpy, pandas, scikit-learn, ray}{Javascript}{Node.js/express,
  frontend/JQuery}

\cvcomputer{Linux}{bash, zsh, git, server/desktop}{\textit{etc.}}{C++,
  (Postre)SQL, MongoDB, Matlab, Java, Lisp, Perl, \LaTeX}

\nocite{*}
\printbibliography[title={Selected Publications}]
\footnotetext{* Indicates equal contributions.}

\end{document}